---
title: "Our Team"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
#install.packages("kableExtra")
library(fontawesome)
library(kableExtra)

library(leaflet)
library(rnaturalearth)
```

<head>
<link rel="preconnect" href="https://fonts.googleapis.com">
<link rel="preconnect" href="https://fonts.gstatic.com" crossorigin>
<link href="https://fonts.googleapis.com/css2?family=Roboto:ital,wght@0,100;0,300;0,400;0,500;0,700;0,900;1,100;1,300;1,400;1,500;1,700;1,900&display=swap" rel="stylesheet">
</head>

# Coordinating Centre

<body>
<table id="example" class="display" style="width:100%">
        <thead>
            <tr>
                <th style="width:50%">Name</th>
                <th>Affiliation</th>
            </tr>
        </thead>
        <tbody>
            <tr>
                <td>A/Prof Monique Kilkenny (Chair) <a href="https://orcid.org/0000-0002-3375-287X" target="_blank">`r fa(name = "orcid", fill = "#a6ce39", height = "1em")`</a></td>
                <td>Monash University</td>
            </tr>
            <tr>
                <td>Prof Dominique Cadilhac <a href="https://orcid.org/0000-0001-8162-682X" target="_blank">`r fa(name = "orcid", fill = "#a6ce39", height = "1em")`</a></td>
                <td>Monash University</td>
            </tr>
            <tr>
                <td>Dr Lachlan Dalli (Coordinator) <a href="https://orcid.org/0000-0003-1449-9132" target="_blank">`r fa(name = "orcid", fill = "#a6ce39", height = "1em")`</a></td>
                <td>Monash University</td>
            </tr>
            <tr>
                <td>Dr Muideen Olaiya (Coordinator) <a href="https://orcid.org/0000-0002-4070-0533" target="_blank">`r fa(name = "orcid", fill = "#a6ce39", height = "1em")`</a></td>
                <td>Monash University</td>
            </tr>
            <tr>
                <td>Dr Joosup Kim <a href="https://orcid.org/0000-0002-4079-0428" target="_blank">`r fa(name = "orcid", fill = "#a6ce39", height = "1em")`</a></td>
                <td>Monash University</td>
            </tr>
        </tbody>
</table>
</body>

# Collaborators

```{r,out.width="100%"  ,echo=FALSE}

world <- ne_countries(scale = "medium", returnclass = "sf")

UK <-world[world$name == "United Kingdom",]
USA <-world[world$admin == "United States of America",]
NZ <- world[world$name == "New Zealand",]
AU <- world[world$name == "Australia",]
CA <- world[world$name == "Canada",]
SW <- world[world$name == "Switzerland",]
CH <- world[world$name == "China",]
PO <- world[world$name == "Poland",]

whole <- rbind(UK,USA,NZ,AU,CA,SW,CH,PO)
whole$people_count <- c(2,3,1,3,6,1,1,1)
whole$popup_text <- 
  paste0('<strong>', whole$subunit, '</strong>',
         '<br/>', 'Collaborators: ', '<strong>', whole$people_count, '</strong>', ' ') %>% 
  lapply(htmltools::HTML)

#palette <- colorNumeric(palette = "YlOrRd", domain = whole$people_count)
  
world_map <- leaflet(whole) %>% addTiles() %>% 
  addMarkers(lng = ~label_x, lat = ~label_y) %>% 
  addPolygons(fillColor = "orange",weight =1,
              color = "white", fillOpacity = 0.7,label = ~popup_text,
              highlight = highlightOptions(weight = 4,
                                       color = "#666",
                                       fillOpacity = 0.7,
                                       bringToFront = TRUE)) 
  

world_map
```

*Collaborators are sorted alphabetically by Surname

### Australia: 

<body>
<table id="example" class="display" style="width:100%">
        <thead>
            <tr>
                <th style="width:50%">Name</th>
                <th>Affiliation</th>
            </tr>
        </thead>
        <tbody>
            <tr>
                <td>Prof Seana Gall <a href="https://orcid.org/0000-0002-5138-2526" target="_blank">`r fa(name = "orcid", fill = "#a6ce39", height = "1em")`</a></td>
                <td>University of Tasmania</td>
            </tr>
            <tr>
                <td>Dr Jenni Ilomäki <a href="https://orcid.org/0000-0002-0348-9441" target="_blank">`r fa(name = "orcid", fill = "#a6ce39", height = "1em")`</a></td>
                <td>Monash University</td>
            </tr>
            <tr>
                <td>Dr Lee Nedkoff <a href="https://orcid.org/0000-0002-3970-625X" target="_blank">`r fa(name = "orcid", fill = "#a6ce39", height = "1em")`</a></td>
                <td>University of Western Australia</td>
            </tr>
        </tbody>
</table>
</body>

### Austria: 

<body>
<table id="example" class="display" style="width:100%">
        <thead>
            <tr>
                <th style="width:50%">Name</th>
                <th>Affiliation</th>
            </tr>
        </thead>
        <tbody>
            <tr>
                <td>MD Julia Ferrari <a href="https://orcid.org/0000-0001-9709-0097" target="_blank">`r fa(name = "orcid", fill = "#a6ce39", height = "1em")`</a></td>
                <td>Department of Neurology, St. John's of God Hospital Vienna</td>
            </tr>
        </tbody>
</table>
</body>

### Canada:  

<body>
<table id="example" class="display" style="width:100%">
        <thead>
            <tr>
                <th style="width:50%">Name</th>
                <th>Affiliation</th>
            </tr>
        </thead>
        <tbody>
            <tr>
                <td>Prof Michael Hill <a href="https://orcid.org/0000-0002-6269-1543" target="_blank">`r fa(name = "orcid", fill = "#a6ce39", height = "1em")`</a></td>
                <td>University of Calgary - Foothills Medical Centre</td>
            </tr>
            <tr>
                <td>Prof Moira Kapral <a href="https://orcid.org/0000-0002-3444-9928" target="_blank">`r fa(name = "orcid", fill = "#a6ce39", height = "1em")`</a></td>
                <td>University of Toronto</td>
            </tr>
            <tr>
                <td>A/Prof Gustavo Saposnik <a href="https://orcid.org/0000-0002-5950-9886" target="_blank">`r fa(name = "orcid", fill = "#a6ce39", height = "1em")`</a></td>
                <td>University of Toronto</td>
            </tr>
            <tr>
                <td>Prof Eric Smith <a href="https://orcid.org/0000-0003-3956-1668" target="_blank">`r fa(name = "orcid", fill = "#a6ce39", height = "1em")`</a></td>
                <td>University of Calgary</td>
            </tr>
            <tr>
                <td>A/Prof Manav Vyas <a href="https://orcid.org/0000-0002-2953-2540" target="_blank">`r fa(name = "orcid", fill = "#a6ce39", height = "1em")`</a></td>
                <td>St. Michael's Hospital - Unity Health Toronto</td>
            </tr>
            <tr>
                <td>Associate Prof Amy Yu <a href="https://orcid.org/0000-0002-7276-9551" target="_blank">`r fa(name = "orcid", fill = "#a6ce39", height = "1em")`</a></td>
                <td>University of Toronto</td>
            </tr>
        </tbody>
</table>
</body>

### China: 

<body>
<table id="example" class="display" style="width:100%">
        <thead>
            <tr>
                <th style="width:50%">Name</th>
                <th>Affiliation</th>
            </tr>
        </thead>
        <tbody>
            <tr>
                <td>Dr Wen-Jun Tu <a href="https://orcid.org/0000-0002-1703-1802" target="_blank">`r fa(name = "orcid", fill = "#a6ce39", height = "1em")`</a></td>
                <td>Beijing Tiantan Hospital, Capital Medical University</td>
            </tr>
        </tbody>
</table>
</body>

### Italy: 

<body>
<table id="example" class="display" style="width:100%">
        <thead>
            <tr>
                <th style="width:50%">Name</th>
                <th>Affiliation</th>
            </tr>
        </thead>
        <tbody>
            <tr>
                <td>Dr Simona Sacco <a href="https://orcid.org/0000-0003-0651-1939" target="_blank">`r fa(name = "orcid", fill = "#a6ce39", height = "1em")`</a></td>
                <td>University of L'Aquila</td>
            </tr>
        </tbody>
</table>
</body>

### New Zealand: 

<body>
<table id="example" class="display" style="width:100%">
        <thead>
            <tr>
                <th style="width:50%">Name</th>
                <th>Affiliation</th>
            </tr>
        </thead>
        <tbody>
            <tr>
                <td>Prof Valery Feigin <a href="https://orcid.org/0000-0002-6372-1740" target="_blank">`r fa(name = "orcid", fill = "#a6ce39", height = "1em")`</a></td>
                <td>Auckland University of Technology</td>
            </tr>
        </tbody>
</table>
</body>

### Poland:

<body>
<table id="example" class="display" style="width:100%">
        <thead>
            <tr>
                <th style="width:50%">Name</th>
                <th>Affiliation</th>
            </tr>
        </thead>
        <tbody>
            <tr>
                <td>Dr Maciej Niewada <a href="https://orcid.org/0000-0002-3730-1996" target="_blank">`r fa(name = "orcid", fill = "#a6ce39", height = "1em")`</a></td>
                <td>Medical University of Warsaw</td>
            </tr>
        </tbody>
</table>
</body>

### Sweden

<body>
<table id="example" class="display" style="width:100%">
        <thead>
            <tr>
                <th style="width:50%">Name</th>
                <th>Affiliation</th>
            </tr>
        </thead>
        <tbody>
            <tr>
                <td>Prof Bo Norrving <a href="https://orcid.org/0000-0002-8024-5096" target="_blank">`r fa(name = "orcid", fill = "#a6ce39", height = "1em")`</a></td>
                <td>Lund University</td>
            </tr>
        </tbody>
</table>
</body>

### Switzerland:

<body>
<table id="example" class="display" style="width:100%">
        <thead>
            <tr>
                <th style="width:50%">Name</th>
                <th>Affiliation</th>
            </tr>
        </thead>
        <tbody>
            <tr>
                <td>Dr Isabelle Arnet <a href="https://orcid.org/0000-0001-7591-4104" target="_blank">`r fa(name = "orcid", fill = "#a6ce39", height = "1em")`</a></td>
                <td>University of Basel</td>
            </tr>
        </tbody>
</table>
</body>

### United Kingdom: 

<body>
<table id="example" class="display" style="width:100%">
        <thead>
            <tr>
                <th style="width:50%">Name</th>
                <th>Affiliation</th>
            </tr>
        </thead>
        <tbody>
            <tr>
                <td>Dr Ben Bray <a href="https://orcid.org/0000-0002-8983-7530" target="_blank">`r fa(name = "orcid", fill = "#a6ce39", height = "1em")`</a></td>
                <td>King’s College London</td>
            </tr>
            <tr>
                <td>Prof William Whiteley <a href="https://orcid.org/0000-0002-4816-8991" target="_blank">`r fa(name = "orcid", fill = "#a6ce39", height = "1em")`</a></td>
                <td>University of Edinburgh</td>
            </tr>
        </tbody>
</table>
</body>

### USA: 

<body>
<table id="example" class="display" style="width:100%">
        <thead>
            <tr>
                <th style="width:50%">Name</th>
                <th>Affiliation</th>
            </tr>
        </thead>
        <tbody>
            <tr>
                <td>Associate Prof Brian Mac Grory <a href="https://orcid.org/0000-0003-3914-8419" target="_blank">`r fa(name = "orcid", fill = "#a6ce39", height = "1em")`</a></td>
                <td>Duke University</td>
            </tr>
            <tr>
                <td>Prof Mat Reeves <a href="https://orcid.org/0000-0002-8019-6343" target="_blank">`r fa(name = "orcid", fill = "#a6ce39", height = "1em")`</a></td>
                <td>Michigan State University</td>
            </tr>
            <tr>
                <td>A/Prof Ying Xian <a href="https://orcid.org/0000-0002-1237-1162" target="_blank">`r fa(name = "orcid", fill = "#a6ce39", height = "1em")`</a></td>
                <td>University of Texas Southwestern Medical Center</td>
            </tr>
        </tbody>
</table>
</body>